nuclear energy in comparison

### 2024-03-25 nuclear in comparison.Rmd
knitted results with mice to pdf

---
title: "nuclear energy in comparison"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
    keep_md: yes
  header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  - \usepackage{pdflscape}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  html_document:
    toc: yes
    toc_depth: '2'
    df_print: paged
---

>>>>

---
title: "nuclear energy in comparison"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
    keep_md: yes
    latex_engine: xelatex
geometry: "left=0.5cm,right=0.5cm,top=0.5cm,bottom=0.5cm"
header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  - \usepackage{pdflscape}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
html_document:
  toc: yes
  toc_depth: '2'
  df_print: paged
---

### 2024-03-25 nuclear-in-comparison.tex
knitted results with mice to pdf

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={nuclear energy in comparison},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

\% Table created by stargazer v.5.2.3 by Marek Hlavac, Social Policy
Institute. E-mail: marek.hlavac at gmail.com \% Date and time: Wed, Jan
10, 2024 - 09:43:59

@@

@@

\hypertarget{net-benefit-by-state}{%
\subsection{Net benefit by state}\label{net-benefit-by-state}}

@@

@@

\includegraphics[width=1\linewidth,height=1\textheight]{nuclear-in-comparison_files/figure-latex/unnamed-chunk-24-1}

@@

\includegraphics[width=1\linewidth,height=1\textheight]{nuclear-in-comparison_files/figure-latex/unnamed-chunk-28-1}

@@

\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-29-1.pdf}
\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-29-2.pdf}

@@

\includegraphics[width=1\linewidth,height=1\textheight]{nuclear-in-comparison_files/figure-latex/unnamed-chunk-32-1}

@@

\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-33-1.pdf}

@@

\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-35-1.pdf}
\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-35-2.pdf}
\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-35-3.pdf}
\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-35-4.pdf}

@@

\% Table created by stargazer v.5.2.3 by Marek Hlavac, Social Policy
Institute. E-mail: marek.hlavac at gmail.com \% Date and time: Wed, Jan
10, 2024 - 09:44:22

@@

@@

\caption{\label{tab:unnamed-chunk-43}Confirmatory Factor Analysis(CFA) on newly developed eco-pol scale}

@@

\cellcolor{gray!6}{People Centered Development} & \cellcolor{gray!6}{Large corporations are destroying the local industries in India and benefiting only a handful of people.} & \cellcolor{gray!6}{0.287} & \cellcolor{gray!6}{0.058} & \cellcolor{gray!6}{4.972} & \cellcolor{gray!6}{7e-07} & \cellcolor{gray!6}{0.1741052} & \cellcolor{gray!6}{0.4007040} & \cellcolor{gray!6}{0.2874046} & \cellcolor{gray!6}{0.2317296}\\

@@

People Centered Development & Regardless of ownership, the government should pass strong regulations and implement them. & 0.296 & 0.052 & 5.733 & 0e+00 & 0.1949541 & 0.3974941 & 0.2962241 & 0.2659785\\

@@

\caption{\label{tab:unnamed-chunk-47}Confirmatory Factor Analysis(CFA) on newly developed eco-pol scale}

@@

\cellcolor{gray!6}{People Centered Development} & \cellcolor{gray!6}{Large corporations are destroying the local industries in India and benefiting only a handful of people.} & \cellcolor{gray!6}{-0.634} & \cellcolor{gray!6}{0.057} & \cellcolor{gray!6}{-11.174} & \cellcolor{gray!6}{0.0e+00} & \cellcolor{gray!6}{-0.7449013} & \cellcolor{gray!6}{-0.5225822} & \cellcolor{gray!6}{-0.6337417} & \cellcolor{gray!6}{-0.5349921}\\

@@

People Centered Development & Regardless of ownership, the government should pass strong regulations and implement them. & -0.509 & 0.054 & -9.351 & 0.0e+00 & -0.6162708 & -0.4027047 & -0.5094877 & -0.4577641\\

>>>>

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={nuclear energy in comparison},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[left=0.5cm,right=0.5cm,top=0.5cm,bottom=0.5cm]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{dcolumn}
\usepackage{array}
\usepackage{pdflscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

\% Table created by stargazer v.5.2.3 by Marek Hlavac, Social Policy
Institute. E-mail: marek.hlavac at gmail.com \% Date and time: Sun, Mar
24, 2024 - 13:05:37

@@

\begin{verbatim}
## List of 5
##  $ Maharashtra  : tibble [14 x 6] (S3: tbl_df/tbl/data.frame)
##   ..$ State     : chr [1:14] "Maharashtra" "Maharashtra" "Maharashtra" "Maharashtra" ...
##   ..$ Tech      : Factor w/ 7 levels "Solar","Wind",..: 5 6 3 7 4 1 2 5 6 3 ...
##   ..$ Mean_Value: num [1:14] 3.27 3.25 2.61 3.16 3.29 ...
##   ..$ sd        : num [1:14] 0.992 1.01 1.032 1.033 1.014 ...
##   ..$ se        : num [1:14] 0.0388 0.0395 0.0404 0.0404 0.0397 ...
##   ..$ Category  : chr [1:14] "Risky" "Risky" "Risky" "Risky" ...
##  $ Rajasthan    : tibble [14 x 6] (S3: tbl_df/tbl/data.frame)
##   ..$ State     : chr [1:14] "Rajasthan" "Rajasthan" "Rajasthan" "Rajasthan" ...
##   ..$ Tech      : Factor w/ 7 levels "Solar","Wind",..: 5 6 3 7 4 1 2 5 6 3 ...
##   ..$ Mean_Value: num [1:14] 3.14 3.33 1.76 3.35 2.19 ...
##   ..$ sd        : num [1:14] 0.945 1.001 1.016 1.144 1.155 ...
##   ..$ se        : num [1:14] 0.0363 0.0385 0.039 0.0439 0.0444 ...
##   ..$ Category  : chr [1:14] "Risky" "Risky" "Risky" "Risky" ...
##  $ Tamil Nadu   : tibble [14 x 6] (S3: tbl_df/tbl/data.frame)
##   ..$ State     : chr [1:14] "Tamil Nadu" "Tamil Nadu" "Tamil Nadu" "Tamil Nadu" ...
##   ..$ Tech      : Factor w/ 7 levels "Solar","Wind",..: 5 6 3 7 4 1 2 5 6 3 ...
##   ..$ Mean_Value: num [1:14] 2.15 2.24 1.46 2.89 2.68 ...
##   ..$ sd        : num [1:14] 1.196 1.417 0.862 1.282 1.296 ...
##   ..$ se        : num [1:14] 0.0668 0.0792 0.0482 0.0717 0.0724 ...
##   ..$ Category  : chr [1:14] "Risky" "Risky" "Risky" "Risky" ...
##  $ Uttar Pradesh: tibble [14 x 6] (S3: tbl_df/tbl/data.frame)
##   ..$ State     : chr [1:14] "Uttar Pradesh" "Uttar Pradesh" "Uttar Pradesh" "Uttar Pradesh" ...
##   ..$ Tech      : Factor w/ 7 levels "Solar","Wind",..: 5 6 3 7 4 1 2 5 6 3 ...
##   ..$ Mean_Value: num [1:14] 2.63 2.46 2.98 2.94 2.84 ...
##   ..$ sd        : num [1:14] 1.052 1.254 1.354 1.265 0.926 ...
##   ..$ se        : num [1:14] 0.0941 0.1122 0.1211 0.1132 0.0828 ...
##   ..$ Category  : chr [1:14] "Risky" "Risky" "Risky" "Risky" ...
##  $ West Bengal  : tibble [14 x 6] (S3: tbl_df/tbl/data.frame)
##   ..$ State     : chr [1:14] "West Bengal" "West Bengal" "West Bengal" "West Bengal" ...
##   ..$ Tech      : Factor w/ 7 levels "Solar","Wind",..: 5 6 3 7 4 1 2 5 6 3 ...
##   ..$ Mean_Value: num [1:14] 3.36 3.63 2.7 4.4 3.23 ...
##   ..$ sd        : num [1:14] 1.05 1.01 1.37 0.72 1.1 ...
##   ..$ se        : num [1:14] 0.0536 0.0517 0.0698 0.0366 0.0558 ...
##   ..$ Category  : chr [1:14] "Risky" "Risky" "Risky" "Risky" ...
\end{verbatim}
## 'data.frame':    2161 obs. of  193 variables:
##  $ Respondent          : int  1 2 3 4 5 6 7 8 9 10 ...
##  $ Language            : chr  "HI" "BN" "BN" "BN" ...
##  $ Survey_Date         : chr  "05-12-2021" "08-12-2021" "08-12-2021" "08-12-2021" ...
##  $ State               : chr  "Uttar Pradesh" "West Bengal" "West Bengal" "West Bengal" ...
##  $ Risky_Hydro         : num  3 1 2 2 4 2 2 NA 3 5 ...
##  $ Risky_Solar         : num  1 1 1 2 1 1 1 2 3 1 ...
##  $ Risky_Wind          : num  1 2 2 2 1 1 1 1 2 3 ...
##  $ Risky_Nuclear       : num  2 4 4 4 5 3 2 4 5 NA ...
##  $ Risky_Coal          : num  3 4 NA 4 5 2 3 2 4 3 ...
##  $ Risky_Gas           : num  3 4 4 3 4 1 3 3 4 5 ...
##  $ Risky_Oil           : num  3 3 2 3 4 2 3 3 4 2 ...
##  $ Risky_INDHydro      : num  3 3 2 2 2 2 2 3 4 5 ...
##  $ Risky_INDSolar      : num  3 1 1 1 5 2 2 3 1 1 ...
##  $ Risky_INDWind       : num  NA 4 5 2 1 NA 3 NA 3 3 ...
##  $ Risky_INDBiogas     : num  3 1 NA 2 2 2 2 NA 3 4 ...
##  $ Risky_INDDiesel     : num  3 2 2 2 4 4 4 2 3 4 ...
##  $ Risky_INDKerosene   : num  NA 1 2 1 3 2 4 2 4 5 ...
##  $ Risky_INDFirewoodetc: num  2 2 1 1 2 1 1 1 3 5 ...
##  $ Risky_INDLPG        : num  5 3 1 1 5 2 2 4 5 5 ...
##  $ Ben_Hydro           : num  4 3 2 2 4 2 2 NA 2 4 ...
##  $ Ben_Solar           : num  4 4 2 3 3 3 3 4 3 3 ...
##  $ Ben_Wind            : num  3 4 2 2 5 1 2 2 5 3 ...
##  $ Ben_Nuclear         : num  5 2 NA 1 1 1 1 4 3 5 ...
##  $ Ben_Coal            : num  5 4 2 1 1 1 1 NA 4 4 ...
##  $ Ben_Gas             : num  1 4 2 1 4 2 1 5 4 4 ...
##  $ Ben_Oil             : num  3 3 2 2 3 1 2 3 5 3 ...
##  $ Ben_INDHydro        : num  5 3 2 2 4 3 2 NA 3 NA ...
##  $ Ben_INDSolar        : num  3 2 NA NA 2 2 1 4 2 5 ...
##  $ Ben_INDWind         : num  2 NA NA 2 2 NA 2 NA 3 3 ...
##  $ Ben_INDDiesel       : num  1 3 2 2 3 1 1 2 3 4 ...
##  $ Ben_INDBiogas       : num  5 NA 2 2 4 3 1 2 5 4 ...
##  $ Ben_INDFirewoodetc  : num  4 3 3 3 1 3 2 2 4 1 ...
##  $ Ben_INDLPG          : num  2 2 3 2 5 2 3 NA NA 1 ...
##  $ Ben_INDKerosene     : num  2 2 3 2 1 2 2 2 NA 2 ...
##  $ N_accept            : num  3 1 1 1 1 2 2 NA NA NA ...
##  $ N_reluctantlyaccept : num  1 2 2 2 NA 2 2 NA NA NA ...
##  $ N_reject            : num  3 NA NA 4 NA 4 4 NA NA NA ...
##  $ K_IINTRFER          : num  4 4 2 5 4 2 3 2 3 1 ...
##  $ K_IPRIVACY          : num  2 NA 2 2 3 3 3 2 4 5 ...
##  $ K_SHARM             : num  5 NA 2 4 5 3 3 1 3 5 ...
##  $ K_IPROTECT          : num  3 4 3 2 1 3 NA 2 3 1 ...
##  $ K_SLIMCHOI          : num  1 5 NA NA 5 NA NA NA 3 5 ...
##  $ K_SPROTECT          : num  2 4 NA NA 3 3 3 2 4 5 ...
##  $ K_HEQUAL            : num  1 2 4 4 4 2 2 5 4 5 ...
##  $ K_HREVDIS1          : num  5 3 3 2 2 3 3 4 4 4 ...
##  $ K_EDISCRIM          : num  NA NA 3 2 4 3 3 NA 5 3 ...
##  $ K_ERADEQ1           : num  5 5 5 5 5 5 1 4 NA 4 ...
##  $ K_EWEALTH           : num  4 NA NA 3 5 3 3 5 NA 4 ...
##  $ K_ERADEQ2           : num  5 5 5 5 1 5 5 5 4 5 ...
##  $ DECISIONDECEN       : num  5 NA NA NA NA 3 3 NA 3 NA ...
##  $ DECISIONCEN         : num  3 3 NA NA NA NA 3 4 NA 4 ...
##  $ SYSTEMTOTAL         : num  1 5 5 3 2 3 3 5 NA 5 ...
##  $ SYSTEMTECHNO        : num  2 NA 3 3 NA 5 NA 4 5 4 ...
##  $ SYSTEMDEMO          : num  2 3 NA NA 5 3 NA 3 3 5 ...
##  $ SYSTEMRELIGION      : num  1 NA NA 3 4 NA NA 3 4 5 ...
##  $ INDUSTRYSMALL       : num  5 5 2 2 5 2 2 4 5 5 ...
##  $ INDUSTRYLARGE       : num  3 4 4 5 5 5 5 5 5 5 ...
##  $ ECONOMYLOCAL        : num  1 2 4 2 1 3 4 4 4 3 ...
##  $ ECONOMYGLOBAL       : num  1 3 3 4 4 NA 1 5 4 4 ...
##  $ DEVOVERENV          : num  1 3 3 NA NA 3 3 4 4 3 ...
##  $ ENVOVERDEV          : num  2 NA NA NA 2 NA 3 4 5 5 ...
##  $ OWNERPVT            : num  4 4 4 3 3 3 NA 1 NA 4 ...
##  $ OWNERPUB            : num  3 NA 2 3 2 2 NA 2 NA 2 ...
##  $ OWNERREG            : num  1 NA 3 5 NA 3 3 5 NA 4 ...
##  $ OWNERNOREG          : num  4 NA NA 3 NA NA 3 5 NA 3 ...
##  $ WEALTHLIM           : num  3 4 3 3 4 NA NA 4 NA 5 ...
##  $ MECHANISATION       : num  4 5 5 5 5 4 5 4 4 5 ...
##  $ DISPLACESOLAR       : num  4 1 1 2 1 2 2 2 2 1 ...
##  $ POLLUTESOLAR        : num  4 1 1 2 1 1 1 1 1 1 ...
##  $ HEALTHSOLAR         : num  NA 2 2 2 1 2 1 1 1 1 ...
##  $ JOBSSOLAR           : num  NA 2 NA NA 1 NA NA 1 3 2 ...
##  $ BEAUTYSOLAR         : num  NA 2 2 1 1 2 1 1 1 1 ...
##  $ PRIDESOLAR          : num  NA 4 2 4 5 2 4 5 4 5 ...
##  $ NPRIDESOLAR         : num  3 4 2 4 4 3 4 5 5 5 ...
##  $ DEVSOLAR            : num  2 2 3 2 5 3 4 5 4 5 ...
##  $ PROSPERSOLAR        : num  2 2 3 3 2 2 3 2 1 4 ...
##  $ RELYSOLAR           : num  4 2 NA 3 NA 3 NA 5 2 4 ...
##  $ DISPLACEROOFS       : num  3 2 2 2 1 2 2 1 2 1 ...
##  $ POLLUTEROOFS        : num  1 2 2 1 1 2 2 1 1 1 ...
##  $ HEALTHROOFS         : num  1 1 2 1 1 2 2 1 1 1 ...
##  $ JOBSROOFS           : num  2 NA NA 3 1 NA NA 1 NA 4 ...
##  $ BEAUTYROOFS         : num  4 2 1 2 1 1 2 1 1 1 ...
##  $ PRIDEROOFS          : num  2 2 2 2 5 3 3 5 4 5 ...
##  $ NPRIDEROOFS         : num  1 NA 2 3 5 3 3 5 NA 5 ...
##  $ DEVROOFS            : num  2 2 2 NA 5 2 4 5 NA 5 ...
##  $ PROSPERROOFS        : num  3 3 1 2 3 3 4 5 NA 5 ...
##  $ RELYROOFS           : num  3 3 3 2 NA 4 4 5 3 4 ...
##  $ DISPLACEDIESEL      : num  1 4 2 2 1 2 4 NA 4 2 ...
##  $ POLLUTEDIESEL       : num  4 2 4 3 1 4 2 5 5 4 ...
##  $ HEALTHDIESEL        : num  NA 3 4 3 2 3 3 4 4 1 ...
##  $ JOBSDIESEL          : num  3 NA NA 4 NA 3 3 1 3 4 ...
##  $ BEAUTYDIESEL        : num  3 4 5 3 2 4 5 4 5 4 ...
##  $ PRIDEDIESEL         : num  2 3 3 2 NA 2 2 4 2 4 ...
##  $ NPRIDEDIESEL        : num  3 3 4 1 1 2 3 4 NA 4 ...
##  $ DEVDIESEL           : num  2 NA 3 1 1 2 NA 2 NA 4 ...
##  $ PROSPERDIESEL       : num  4 3 3 2 1 4 5 3 5 5 ...
##  $ RELYDIESEL          : num  1 3 4 2 NA 3 NA 4 NA 4 ...
##  $ DISPLACEFIRE        : num  4 1 2 2 4 4 3 2 2 4 ...
##  $ POLLUTEFIRE         : num  2 1 1 2 3 2 1 3 2 4 ...
##   [list output truncated]

@@

\hypertarget{maharshtra-t-tests}{%
\section{Maharshtra t tests}\label{maharshtra-t-tests}}

\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-19-1.pdf}

\hypertarget{tamil-nadu-t-tests}{%
\section{Tamil Nadu t tests}\label{tamil-nadu-t-tests}}

@@

\hypertarget{uttar-pradesh-t-tests}{%
\section{Uttar Pradesh t tests}\label{uttar-pradesh-t-tests}}

\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-21-1.pdf}

\hypertarget{rajasthan-t-tests}{%
\section{Rajasthan t tests}\label{rajasthan-t-tests}}

\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-22-1.pdf}

\hypertarget{west-bengal-t-tests}{%
\section{West Bengal t tests}\label{west-bengal-t-tests}}

\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-23-1.pdf}
\#\# Net benefit by state

\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-25-1.pdf}

@@

\includegraphics[width=1\linewidth,height=1\textheight]{nuclear-in-comparison_files/figure-latex/unnamed-chunk-29-1}

@@

\includegraphics[width=1\linewidth,height=1\textheight]{nuclear-in-comparison_files/figure-latex/unnamed-chunk-33-1}

@@

\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-34-1.pdf}
\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-34-2.pdf}

@@

\includegraphics[width=1\linewidth,height=1\textheight]{nuclear-in-comparison_files/figure-latex/unnamed-chunk-37-1}

@@

\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-38-1.pdf}

@@

\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-40-1.pdf}
\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-40-2.pdf}
\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-40-3.pdf}
\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-40-4.pdf}

@@

\% Table created by stargazer v.5.2.3 by Marek Hlavac, Social Policy
Institute. E-mail: marek.hlavac at gmail.com \% Date and time: Sun, Mar
24, 2024 - 13:06:02

@@

## ========================================================================================================================================================================
##                     ----------------------------------------------------------------------------------------------------------------------------------------------------
## ------------------------------------------------------------------------------------------------------------------------------------------------------------------------
## Uppercaste                  -0.135**                  -0.006                   -0.056                   0.026                   -0.146*                  -0.021         
##                             (0.061)                  (0.051)                  (0.058)                  (0.089)                  (0.084)                  (0.075)        
## Male                         0.045                    -0.047                   0.015                    0.008                    0.058                   -0.016         
##                             (0.062)                  (0.053)                  (0.059)                  (0.092)                  (0.087)                  (0.078)        
## Hindu                        -0.047                   -0.057                   0.099                   0.362***                 0.290***                 -0.008         
##                             (0.070)                  (0.059)                  (0.066)                  (0.100)                  (0.095)                  (0.085)        
## UrbanUrban                   0.052                    -0.076                   0.055                    0.172*                   0.143                    0.014         
##                             (0.067)                  (0.056)                  (0.063)                  (0.099)                  (0.093)                  (0.084)        
## age                          -0.015                  0.045**                  0.053**                   -0.008                   0.045                   -0.035         
##                             (0.027)                  (0.023)                  (0.025)                  (0.043)                  (0.040)                  (0.036)        
## StateRajasthan              0.222**                 -1.285***                 0.234***                  -0.014                  1.957***                  0.077         
##                             (0.094)                  (0.080)                  (0.090)                  (0.135)                  (0.128)                  (0.115)        
## StateTamil Nadu             -0.242**                -1.547***                -1.103***                -0.625***                 2.027***                0.795***        
##                             (0.099)                  (0.084)                  (0.094)                  (0.191)                  (0.181)                  (0.162)        
## StateUttar Pradesh           -0.178                 -1.344***                -0.638***                  -0.250                  1.612***                 0.296**        
##                             (0.120)                  (0.102)                  (0.114)                  (0.177)                  (0.168)                  (0.151)        
## StateWest Bengal            1.276***                -1.330***                  0.071                  -1.522***                 1.853***                -0.222**        
##                             (0.083)                  (0.071)                  (0.079)                  (0.125)                  (0.118)                  (0.106)        
## Constant                    3.208***                 2.752***                 3.053***                  -0.240                  0.323**                   0.022         
##                             (0.100)                  (0.084)                  (0.095)                  (0.147)                  (0.139)                  (0.124)        
## ------------------------------------------------------------------------------------------------------------------------------------------------------------------------
## R2                           0.204                    0.353                    0.141                    0.171                    0.338                    0.035         
## Adjusted R2                  0.199                    0.349                    0.136                    0.165                    0.333                    0.028         
## Residual Std. Error    1.057 (df = 1434)        0.894 (df = 1434)        1.004 (df = 1434)        1.413 (df = 1173)        1.334 (df = 1173)        1.199 (df = 1173)   
## F Statistic         40.720*** (df = 9; 1434) 86.983*** (df = 9; 1434) 26.208*** (df = 9; 1434) 26.873*** (df = 9; 1173) 66.499*** (df = 9; 1173) 4.789*** (df = 9; 1173)
## ========================================================================================================================================================================

@@

\caption{\label{tab:unnamed-chunk-49}Confirmatory Factor Analysis(CFA) on newly developed eco-pol scale}

@@

\cellcolor{gray!6}{People Centered Development} & \cellcolor{gray!6}{Large corporations are destroying the local industries in India and benefiting only a handful of people.} & \cellcolor{gray!6}{-0.287} & \cellcolor{gray!6}{0.058} & \cellcolor{gray!6}{-4.972} & \cellcolor{gray!6}{7e-07} & \cellcolor{gray!6}{-0.4007040} & \cellcolor{gray!6}{-0.1741052} & \cellcolor{gray!6}{-0.2874046} & \cellcolor{gray!6}{-0.2317296}\\

@@

People Centered Development & Regardless of ownership, the government should pass strong regulations and implement them. & -0.296 & 0.052 & -5.733 & 0e+00 & -0.3974941 & -0.1949541 & -0.2962241 & -0.2659785\\

@@

\caption{\label{tab:unnamed-chunk-53}Confirmatory Factor Analysis(CFA) on newly developed eco-pol scale}

@@

\cellcolor{gray!6}{People Centered Development} & \cellcolor{gray!6}{Large corporations are destroying the local industries in India and benefiting only a handful of people.} & \cellcolor{gray!6}{0.634} & \cellcolor{gray!6}{0.057} & \cellcolor{gray!6}{11.174} & \cellcolor{gray!6}{0.0e+00} & \cellcolor{gray!6}{0.5225822} & \cellcolor{gray!6}{0.7449013} & \cellcolor{gray!6}{0.6337417} & \cellcolor{gray!6}{0.5349921}\\

@@

People Centered Development & Regardless of ownership, the government should pass strong regulations and implement them. & 0.509 & 0.054 & 9.351 & 0.0e+00 & 0.4027047 & 0.6162708 & 0.5094877 & 0.4577641\\
